A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-31 src/tex/ms.tex

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{{\bf Key takeaway:} the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall. In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall. \todo{Replace APOGEE medians with modes and errors on the mode}}
    \label{fig:onezone-dtd}
\end{figure}

>>>>

Figure \ref{fig:yield-outflow} illustrates the effect of the yield scaling on the abundance evolution in one-zone models. All models feature a rapid dilution of the ISM metallicity by $\sim0.5-0.8$ dex, visible in the top two panels, brought on by the infall of pristine gas at $t_{\rm max}$. For the model with $y/Z_\odot=1$, this dilution persists for some time and the metallicity does not return to Solar until the present day. The models with higher yields and outflows recover from this dilution more quickly, returning to Solar metallicity by $\sim5$ Gyr ago. However, the high-yield models experience a decline in [O/Fe] of $\sim0.2$ dex between the second infall and the present day, contrasted with the smaller decline of $\sim0.1$ dex in the low-yield model.

Figure \ref{fig:yield-outflow} also indicates the mode of the APOGEE abundance distributions in 1 Gyr-wide age bins. As explained by \citet{johnson_milky_2024}, the mode is expected to be less sensitive to the effects of radial migration than other statistical measures. The data show that the evolution in [O/H] is close to flat over the past 5 Gyr. The behavior of the $y/Z_\odot=2$ and $y/Z_\odot=3$ models closely matches this trend in the data, whereas the $y/Z_\odot=1$ model shows significant evolution of $\sim0.2$ dex during the same time period. The [Fe/H] abundance in the data does increase slightly at late times, likely due to the delayed contribution of Fe from SNe Ia. Between lookback times of $\sim5-9$ Gyr, the modes of [O/H] and [Fe/H] are actually higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times. The

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{The abundance evolution of three one-zone models with different yield and outflow settings. Table \ref{tab:yields} presents the population-averaged yields for each model. The gray points with error bars indicate the mode of the APOGEE abundances from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq|z|\leq0.5$ kpc) binned by the \citet{leung_variational_2023} age estimates.}
    \label{fig:yield-outflow}
\end{figure}
